Dataflow-Guided Filtering for Efficient and Adjustable Run-Time Monitoring

### 2014-05-28 title.tex
Updates to intro and related work.
Changed title. Edited intro.
Update abstract.

\title{
Using Dynamic Dataflow Tracking to Reduce Overheads for \\ Parallel
Run-Time Monitoring
}

@@

Recent studies have proposed various parallel run-time monitoring techniques to
improve the reliability, security, and debugging capabilities of
computer systems. These run-time monitors introduce overheads in performance
and energy to the system. Traditionally, these overheads have been an
all-or-nothing cost; monitoring cannot be used if the overheads are considered too large.
% where if monitoring is enabled, then the program will incur, in full, the
% associated overheads. 
%That is, if the overheads are considered too large, then monitoring cannot be
%enabled. 
In this paper, we present a run-time monitoring architecture that
enables a trade-off between the coverage and the overheads.
The system allows an overhead or coverage target to be specified,
and limits the amount of monitoring performed at run-time to meet the target. 
However, simply skipping monitoring operations can lead to false
positives, signaling errors when none have occurred. Our proposed architecture
prevents false positives using a method that invalidates certain metadata
when monitoring is not performed. Dedicated hardware that performs dynamic
information flow tracking (DIFT) is used to propagate this invalidation
information in order to prevent false positives. In addition, we can use this
DIFT hardware to also track the presence of valid metadata. This allows us to
filter out events in order to reduce monitoring overheads.
% Our experiments show that the system is able to
% closely meet the target overhead and achieve significant monitoring coverage
% for reasonable overhead targets.
In our experiments, we see that the system is able to come
within 2\% of the specified execution time overhead in almost all cases.  In addition, with a
performance overhead target of 10\%, 49-90\% of monitoring coverage is achieved
on average depending on the monitoring technique.

>>>>

\title{
Dataflow-Guided Filtering for Efficient and Adjustable Run-Time Monitoring
}

@@

Recent studies have proposed various parallel run-time monitoring techniques to
improve the reliability, security, and debugging capabilities of computer
systems. These run-time monitors can introduce large overheads in performance
and energy to the system.  Traditionally, these overheads have been an
all-or-nothing cost; monitoring cannot be used if the overheads are considered
too large.  In this paper, we show how a hardware-based dataflow tracking
engine can be used to filter out unnecessary monitoring and to enable partial
monitoring.  We are able to filter out unnecessary monitoring related to clean
metadata in order to greatly reduce the overheads of monitoring. In addition,
we present a hardware architecture can further reduce overheads by enabling a
trade-off between the amount of monitoring performed and the overheads
incurred. In order to prevent false positives due to this partial monitoring,
we extend the dataflow engine to track dropped monitoring flows. We investigate
some of the trade-offs involved with partial monitoring in terms of how closely
an overhead target can be matched versus the coverage that can be achieved.
% Our experiments show that the system is able to
% closely meet the target overhead and achieve significant monitoring coverage
% for reasonable overhead targets.
In our experiments, we see that filtering is able to decrease monitoring
overheads from XX\%-XX\% on average, depending on the monitoring scheme, to
XX\%-XX\%. Additionally, we are able to still achieve XX\% coverage with a 10\%
overhead target.
